Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-31 doc/paper.tex
Add more paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>
Filling in Approach part
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

Using this environment, we explore three different ways of training the agent. We evaluate these models on the same Minigrid environments and compare their performance against each other.\\

@@

As we can see from figure \ref{doorkeyresults}, LLM integration gives a noticable improvement to the performance of the model, not just in the early stages of training, but throughout the entire training process. Averaging over all episodes of all eight runs per model, we find that LLM reward shaping receives $24\%$ more reward per episode than PPO trained without LLM rewards. Furthermore, this is an improvement that comes at very little computational cost, because LLM responses can be cached between runs. Of the eight runs on this environment using LLM reward shaping, the last three runs never queried the LLM at all, only relying on the cache of previous answers. In all methods, we see that the variance is very large ($0.28$ and $0.31$ for LLM reward shaping and baseline, respectively). Given that there is no reward given for a partially completed task, this is not unexpected.

>>>>

To evaluate the effectivness of the integration of LLMs into reinfrocement learning algorithms, er use the \textbf{MiniGrid} and \textbf{BabyAI} libraries, we handpick specific environments with varying levels of complexity, to evaluate the effectivness of our proposed techniques against a standard proximal policy optimzation agent and each other. The environments are all based in a small sized grid-world, where the agent is surrounded by walls, and has to perform some form of task to complete the game. How difficult an environment is to beat, depends no factors such as shape of the walls, if the agent has to solve subtasks to finish the game, and the type of subtasks encountered. Moreover what makes these environments exceptionally well suited for testing our approach, is that they are sparse in that the agent will only receive a reward when it finishes the game. It is a well known fact that even the PPO algorithm struggles in very complex and sparse environments, hence it becomes the perfect arena to see if the high generalization capabilites of Large pre-trained Language Models will lead to better results than using only RL methods.

@@

As we can see from figure \ref{doorkeyresults}, LLM integration gives a noticable improvement to the performance of the model, not just in the early stages of training, but throughout the entire training process. Averaging over all episodes of all eight runs per model, we find that LLM reward shaping receives $24\%$ more reward per episode than PPO trained without LLM rewards. Furthermore, this is an improvement that comes at very little computational cost, because LLM responses can be cached between runs. Of the eight runs on this environment using LLM reward shaping, the last three runs never queried the LLM at all, only relying on the cache of previous answers. In all methods, we see that the standard deviation is very large ($0.28$ and $0.31$ for LLM reward shaping and baseline, respectively). Given that there is no reward given for a partially completed task, this is not unexpected.
